An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-10-25 neurips-19/poly-embed.tex
more inline comments

\subsection{Notation and Losses}

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.
\raft{CHANGED}
To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low dimension $d$ above.

\subsection{Property Elicitation}

@@

\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.  In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.  Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.  Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

\subsection{Links and Embeddings}

@@

@@

\raf{Will shorten.}
\proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.  They are generally derived mathematically, rather than computationally.  These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for several discussions early on, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for his help with Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

>>>>

\subsection{Notation and Losses}
\label{sec:notation-losses}

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
\raft{ADDED}
We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.
\raft{ADDED}
To motivate our focus on polyhedral losses, we echo Ramaswamy et al.~\cite[Section 1.2]{ramaswamy2018consistent}, who note that smooth surrogates often encode much more information than necessary, and in these cases non-smooth surrogates are the only candidates to achieve a low dimension $d$ above.

\subsection{Property Elicitation}
\label{sec:property-elicitation}

@@

\raf{I am not sure this is the place to clarify these connections.  I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.  If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.  E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.  Jessie, feel free to give it a shot.}
\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.  In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.  Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.  Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

\subsection{Links and Embeddings}
\label{sec:links-embeddings}

@@

Note that the construction given above in Definition~\ref{def:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
We illustrate this formulaic approach in \S~\ref{sec:abstain}.
% \proposedadd{In general, we are not overly concerned with the computational complexity of computing the surrogate and link, since these calculations only need to be computed once.  They are generally derived mathematically, rather than computationally.  These symbolic calculations typically tend to be straightforward, but can sometimes be tricky.}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
\raf{Is this in response to some reviewer, or just because we had to comment stuff for space?}
\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for many early discussions, which led to several important insights.
% to a proof of %\raf{1-d reduction} among other insights.
% Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
We thank Eric Balkanski for help with a lemma about submodular functions. %Lemma~\ref{lem:bar-f}\jessie{We don't have the Lov\'asz hinge appendix here?}.
This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}
